### 2023-10-09 latex/paper/main.tex
figure placement

\usepackage[margin=3cm]{geometry}
\usepackage{listings}
\usepackage{xcolor}

@@

\begin{figure}
    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/det_2_10_3.png}
    \label{fig:det}
    \caption{Determinant}

    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/det_2_10_3_detail.png}
    \label{fig:det_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/dot_2_30_5.png}
    \label{fig:dot}
    \caption{Dot product}

    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/dot_2_30_5_detail.png}
    \label{fig:dot_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/inv_2_8_3.png}
    \label{fig:inv}
    \caption{Inverse}

    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/inv_2_8_3_detail.png}
    \label{fig:inv_detail}
    \caption{Detailed plot}
\end{figure}

\subsection{Rank}
\begin{figure}
    \includegraphics[width=0.8\textwidth, keepaspectratio, center]{img/rank_2_500_5.png}
    \label{fig:rank}
    \caption{Rank}
\end{figure}

>>>>

\usepackage{float}
\usepackage[margin=3cm]{geometry}
\usepackage{listings}
\usepackage{xcolor}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/det_2_10_3.png}
    \centering
    \label{fig:det}
    \caption{Determinant}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/det_2_10_3_detail.png}
    \centering
    \label{fig:det_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/dot_2_30_5.png}
    \centering
    \label{fig:dot}
    \caption{Dot product}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/dot_2_30_5_detail.png}
    \centering
    \label{fig:dot_detail}
    \caption{Detailed plot}
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/inv_2_8_3.png}
    \centering
    \label{fig:inv}
    \caption{Inverse}

    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/inv_2_8_3_detail.png}
    \centering
    \label{fig:inv_detail}
    \caption{Detailed plot}
\end{figure}

\subsection{Rank}
\begin{figure}[H]
    \includegraphics[width=0.8\textwidth, keepaspectratio]{img/rank_2_500_5.png}
    \centering
    \label{fig:rank}
    \caption{Rank}
\end{figure}
